\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-12-19 docs/papers/sto/so.tex
FIXUP draft update figures

\begin{figure*}
  \centering
  \includegraphics[width=.8\columnwidth]{sobol0snap120epoch300.pdf}
  \caption{The transfer function $T$ and correlation coefficient $r$ of the
  \GADGET\ and \pmwd\ simulated density fields, with and without force
  sharpening.
  Sobol 0 snap 120}
  \label{fig:tfcc}
\end{figure*}

% transfer function & correlation coefficient
To compare two fields $\hat f$ and $f$, we introduce for each mode the square
root ratio of power
%
\begin{equation}
T(\vk) \triangleq
\sqrt{\frac{|\hat f(\vk)|^2}{|f(\vk)|^2}},
\label{T}
\end{equation}
%
which is also referred to as the transfer function, and the cross correlation
coefficient
%
\begin{equation}
r(\vk) \triangleq
\frac{\Re \bigl[ \hat f(\vk) f^*(\vk) \bigr]}
     {\sqrt{|\hat f(\vk)|^2 |f(\vk)|^2}}.
\label{r}
\end{equation}
%
The two fields are identical when both $T$ and $r$ are unity.
The PM method is accurate on scales much larger than the cell size, therefore we
expect $T$ and $r$ to be very close to being unity both before and after force
sharpening optimization.

@@

\subsection{Dark Matter Halo Catalogs}

@@

We use Optuna \citep{optuna_2019} to search for the optimal Hyperparameters.

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=.8\columnwidth]{tf_snap120_3063821_e888.pdf} \\
  \includegraphics[width=.8\columnwidth]{cc_snap120_3063821_e888.pdf}
  \caption{The transfer function $T$ and correlation coefficient $r$ of the
  \GADGET\ and \pmwd\ simulated density fields, with and without force
  sharpening. The solid line and shaded region indicate the mean and standard
  deviation of the 64 Sobol simulation setups. mesh shape=1}
  \label{fig:tfcc}
\end{figure*}

% transfer function & correlation coefficient
To compare two fields $\hat f$ and $f$, we introduce for each mode the square
root ratio of the power spectrum
%
\begin{equation}
T(\vk) \triangleq
\sqrt{\frac{|\hat f(\vk)|^2}{|f(\vk)|^2}},
\label{T}
\end{equation}
%
which is also referred to as the transfer function, and the cross correlation
coefficient
%
\begin{equation}
r(\vk) \triangleq
\frac{\Re \bigl[ \hat f(\vk) f^*(\vk) \bigr]}
     {\sqrt{|\hat f(\vk)|^2 |f(\vk)|^2}}.
\label{r}
\end{equation}
%
The two fields are identical when both $T$ and $r$ are unity.
The PM method is accurate on scales much larger than the cell size, therefore we
expect $T$ and $r$ to be very close to being unity both before and after force
sharpening optimization.
To show the $T$ and $r$ for different box sizes, we normalize the wavenumber by
the Nyquist wavenumber $k_{\rm Nyquist}$ of the particle grid.
\YZ{We show T and r separately for different mesh shapes?}

@@

\subsection{Dark Matter Halos}

@@

We use Optuna \citep{optuna_2019} to search for the optimal hyperparameters.
